---
title: "The PODS final project --FDS 2017/2018--"
author: "Davide Aureli, Valerio Guarrasi and Andrea Marcocchia"
date: "12/02/2018"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

# Library
Here we load the library used in the code: 

*"xboost" is used to make the model with the Xboost method
*"glmnet" is used to make the model with the Lasso method. Glmnet is a package that fits a generalized linear model via penalized maximum likelihood. 
*"dplyr"  is used to use the  %>% command and, more in general, a flexible grammar of data manipulation.
*"mice"   is used to replace NA with an imputational method

```{r Load_Libraries}
library(xgboost)
require(dplyr)
library(mice)
library(glmnet)
```

# Load data

We load the train and test datasets, from the Kaggle Competition:
"https://www.kaggle.com/c/house-prices-advanced-regression-techniques/data"

```{r Load_Train_and_Test}
train = read.csv("train.csv", stringsAsFactors=FALSE)
test = read.csv("test.csv", stringsAsFactors=FALSE)
```

#FUNCTIONS Used

We write four functions to change our datasets. This functions are:

* clean_data()
* drop_NA()
* drop_var()
* create_interaction()

We make these operations in both train and test datasets, and so we prefer to write a function for each operation, and after only apply it.
 
## Clean data

Here we group and transform categorical variables.
We start on the train dataset.

At the beginning we tried to group the variables in categories referring to the sale price. But in this way we lost information. So we decided to transform the categorical variables in factorial without grouping them. So each observations has its respective value.

For example: at the begining the neighborhoods that have houses with similar prices were grouped in the same category. Now each neighborhood has a different factor.

Sometimes the value is missing (NA) on purpose. This means that that house is missing that features, so here we assigned the value 0. 
Otherwise, when the observations have a specific meaning, we assign values starting from 1 to the number of different observations.

```{r Clean_Function}
clean_data <- function(df){
  
# attach function to prevent on always writing df$variable_name
# With this command we can directly write variable_name
attach(df)

# Group for Heating
df$riscaldamento[Heating=="GasA"] = 6
df$riscaldamento[Heating=="GasW"] = 5
df$riscaldamento[Heating=="Floor"] = 4
df$riscaldamento[Heating=="Grav"] = 3
df$riscaldamento[Heating=="OthW"] = 2
df$riscaldamento[Heating=="Wall"] = 1  

# Group for LotShape
df$forma_casa[LotShape == "Reg"] = 4
df$forma_casa[LotShape == "IR1"] = 3
df$forma_casa[LotShape == "IR2"] = 2
df$forma_casa[LotShape == "IR3"] = 1

# Group for BsmtQual
df$q_cantina[BsmtQual == "Ex"] = 4
df$q_cantina[BsmtQual == "Gd"] = 3
df$q_cantina[BsmtQual == "TA"] = 2
df$q_cantina[BsmtQual == "Fa"] = 1
df$q_cantina[is.na(BsmtQual)] = 0

# Group for BsmtCond
df$c_cantina[BsmtCond == "Gd"] = 4
df$c_cantina[BsmtCond == "TA"] = 3
df$c_cantina[BsmtCond == "Fa"] = 2
df$c_cantina[is.na(BsmtCond)] = 0
df$c_cantina[BsmtCond == "Po"] = 1

# Group for LandContour
df$altide[LandContour == "Lvl"] = 4
df$altide[LandContour == "Low"] = 3
df$altide[LandContour == "Bnk"] = 2
df$altide[LandContour == "HLS"] = 1

# Group for LotConfig
df$vicolo_cieco[LotConfig =="CulDSac"] = 5
df$vicolo_cieco[LotConfig =="FR3"] = 4
df$vicolo_cieco[LotConfig =="FR2"] = 3
df$vicolo_cieco[LotConfig =="Inside"] = 2
df$vicolo_cieco[LotConfig =="Corner"] = 1

# Group for BldgType
df$dimora[df$BldgType=="1Fam"] = 5
df$dimora[df$BldgType=="TwnhsE"] = 4
df$dimora[df$BldgType=="2fmCon"] = 3
df$dimora[df$BldgType=="Duplex"] = 2
df$dimora[df$BldgType=="Twnhs"] = 1

# Group for RoofStyle
df$copertura_tetto[RoofStyle =="Hip"] = 6
df$copertura_tetto[RoofStyle == "Shed"] = 5
df$copertura_tetto[RoofStyle == "Flat"] = 4
df$copertura_tetto[RoofStyle == "Gable"] = 3
df$copertura_tetto[RoofStyle == "Gambrel"] = 2
df$copertura_tetto[RoofStyle == "Mansard"] = 1

# Group for RoofMatl
df$sostanza_tetto[RoofMatl=="Membran"] = 8
df$sostanza_tetto[RoofMatl=="WdShake"] = 7
df$sostanza_tetto[RoofMatl == "WdShngl"] = 6
df$sostanza_tetto[RoofMatl == "ClyTile"] = 5
df$sostanza_tetto[RoofMatl == "CompShg"] = 4
df$sostanza_tetto[RoofMatl == "Metal"] = 3
df$sostanza_tetto[RoofMatl == "Roll"] = 2
df$sostanza_tetto[RoofMatl == "Tar&Grv"] = 1

# Group for Street
df$vialetto[Street == "Pave"] = 2
df$vialetto[Street == "Grvl"] = 1

# Group for Neighborhood
df$vicinato[Neighborhood=="Blueste"] = 25
df$vicinato[Neighborhood=="BrDale"] = 24
df$vicinato[Neighborhood=="BrkSide"] = 23
df$vicinato[Neighborhood=="Edwards"] = 22
df$vicinato[Neighborhood=="IDOTRR"] = 21
df$vicinato[Neighborhood=="MeadowV"] = 20
df$vicinato[Neighborhood=="OldTown"] = 19
df$vicinato[Neighborhood=="Sawyer"] = 18
df$vicinato[Neighborhood=="Blmngtn"] = 17
df$vicinato[Neighborhood=="CollgCr"] = 16
df$vicinato[Neighborhood=="Gilbert"] = 15
df$vicinato[Neighborhood=="Mitchel"] = 14
df$vicinato[Neighborhood=="NAmes"] = 13
df$vicinato[Neighborhood=="NPkVill"] = 12
df$vicinato[Neighborhood=="NWAmes"] = 11
df$vicinato[Neighborhood=="SawyerW"] = 10
df$vicinato[Neighborhood=="SWISU"] = 9
df$vicinato[Neighborhood=="ClearCr"] = 8
df$vicinato[Neighborhood=="Crawfor"] = 7
df$vicinato[Neighborhood=="NoRidge"] = 6
df$vicinato[Neighborhood=="NridgHt"] = 5
df$vicinato[Neighborhood=="Somerst"] = 4
df$vicinato[Neighborhood=="StoneBr"] = 3
df$vicinato[Neighborhood=="Timber"] = 2
df$vicinato[Neighborhood=="Veenker"] = 1

# Group for HouseStyle
df$stile_casa[HouseStyle =="1.5Unf"] = 8
df$stile_casa[HouseStyle =="SFoyer"] = 7
df$stile_casa[HouseStyle =="1.5Fin"] = 6
df$stile_casa[HouseStyle =="1Story"] = 5
df$stile_casa[HouseStyle =="2.5Unf"] = 4
df$stile_casa[HouseStyle =="SLvl"] = 3
df$stile_casa[HouseStyle =="2.5Fin"] = 2
df$stile_casa[HouseStyle =="2Story"] = 1

# Group for Exterior1st
df$mura1[Exterior1st=="AsbShng"] = 15
df$mura1[Exterior1st=="AsphShn"] = 14
df$mura1[Exterior1st=="BrkComm"] = 13
df$mura1[Exterior1st=="CBlock"] = 12
df$mura1[Exterior1st=="BrkFace"] = 11
df$mura1[Exterior1st=="HdBoard"] = 10
df$mura1[Exterior1st=="MetalSd"] = 9
df$mura1[Exterior1st=="Plywood"] = 8
df$mura1[Exterior1st=="Stucco"] = 7
df$mura1[Exterior1st=="Wd Sdng"] = 6
df$mura1[Exterior1st=="WdShing"] = 5
df$mura1[Exterior1st=="CemntBd"] = 4
df$mura1[Exterior1st=="ImStucc"] = 3
df$mura1[Exterior1st=="Stone"] = 2
df$mura1[Exterior1st=="VinylSd"] = 1

# Group for Exterior2nd
df$mura2[Exterior2nd =="AsbShng"] = 16
df$mura2[Exterior2nd =="AsphShn"] = 15
df$mura2[Exterior2nd =="Brk Cmn"] = 14
df$mura2[Exterior2nd =="CBlock"] = 13
df$mura2[Exterior2nd =="BrkFace"] = 12
df$mura2[Exterior2nd =="HdBoard"] = 11
df$mura2[Exterior2nd =="MetalSd"] = 10
df$mura2[Exterior2nd =="Plywood"] = 9
df$mura2[Exterior2nd =="Stone"] = 8
df$mura2[Exterior2nd =="Stucco"] = 7
df$mura2[Exterior2nd =="Wd Sdng"] = 6
df$mura2[Exterior2nd =="Wd Shng"] = 5
df$mura2[Exterior2nd =="CmentBd"] = 4
df$mura2[Exterior2nd =="ImStucc"] = 3
df$mura2[Exterior2nd =="Other"] = 2
df$mura2[Exterior2nd =="VinylSd"] = 1

# Group for Utilities
df$egws[Utilities == "AllPub"] = 2
df$egws[Utilities == "NoSeWa"] = 1

# Group for LandSlope
df$pendenza[LandSlope == "Gtl"] = 3
df$pendenza[LandSlope == "Mod"] = 2
df$pendenza[LandSlope == "Sev"] = 1

# Group for MasVnrType
df$mur_est1[MasVnrType=="Stone"] = 4
df$mur_est1[MasVnrType=="BrkFace"] = 3
df$mur_est1[is.na(MasVnrType)] = 0
df$mur_est1[MasVnrType=="BrkCmn"] = 2
df$mur_est1[MasVnrType=="None"] = 1

# Group for ExterQual
df$q_est[ExterQual == "Ex"] = 4
df$q_est[ExterQual == "Gd"] = 3
df$q_est[ExterQual == "TA"] = 2
df$q_est[ExterQual == "Fa"] = 1

# Group for ExterCond
df$c_est[ExterCond == "Ex"] = 5
df$c_est[ExterCond == "Gd"] = 4
df$c_est[ExterCond == "TA"] = 3
df$c_est[ExterCond == "Fa"] = 2
df$c_est[ExterCond == "Po"] = 1

# Group for Foundation
df$cement_fdta[Foundation == "PConc"] = 6
df$cement_fdta[Foundation == "BrkTil"] = 5
df$cement_fdta[Foundation == "CBlock"] = 4
df$cement_fdta[Foundation == "Slab"] = 3
df$cement_fdta[Foundation == "Stone"] = 2
df$cement_fdta[Foundation == "Wood"] = 1

# Group for BsmtExposure
df$e_cantina[BsmtExposure == "Gd"] = 4
df$e_cantina[BsmtExposure == "Av"] = 3
df$e_cantina[BsmtExposure == "Mn"] = 2
df$e_cantina[BsmtExposure == "No"] = 1
df$e_cantina[is.na(BsmtExposure)] = 0

# Group for BsmtFinType1
df$f1_cantina[BsmtFinType1 == "GLQ"] = 6
df$f1_cantina[BsmtFinType1 == "Unf"] = 5
df$f1_cantina[BsmtFinType1 == "ALQ"] = 4
df$f1_cantina[BsmtFinType1=="BLQ"] = 3
df$f1_cantina[BsmtFinType1=="Rec"] = 2
df$f1_cantina[BsmtFinType1=="LwQ"] = 1
df$f1_cantina[is.na(BsmtFinType1)] = 0

# Group for BsmtFinType2
df$f2_cantina[BsmtFinType2 == "ALQ"] = 6
df$f2_cantina[BsmtFinType2 == "Unf"] = 5
df$f2_cantina[BsmtFinType2 == "GLQ"] = 4
df$f2_cantina[BsmtFinType2=="Rec"] = 3
df$f2_cantina[BsmtFinType2=="LwQ"] = 2
df$f2_cantina[BsmtFinType2 == "BLQ"] = 1
df$f2_cantina[is.na(BsmtFinType2)] = 0

# Group for HeatingQC
df$q_riscaldamento[HeatingQC == "Ex"] = 5
df$q_riscaldamento[HeatingQC == "Gd"] = 4
df$q_riscaldamento[HeatingQC == "TA"] = 3
df$q_riscaldamento[HeatingQC == "Fa"] = 2
df$q_riscaldamento[HeatingQC == "Po"] = 1

# Group for CentralAir
df$aria[CentralAir == "Y"] = 1
df$aria[CentralAir == "N"] = 0

# Group for Electrical
df$s_corrente[Electrical == "SBrkr" ] = 5
df$s_corrente[is.na(df$Electrical)] = 0
df$s_corrente[Electrical == "FuseA"] = 3
df$s_corrente[Electrical == "FuseF"] = 2
df$s_corrente[Electrical == "FuseP"] = 1
df$s_corrente[Electrical == "Mix"] = 4

# Group for KitchenQual
df$cucina[KitchenQual == "Ex"] = 4
df$cucina[KitchenQual == "Gd"] = 3
df$cucina[KitchenQual == "TA"] = 2
df$cucina[KitchenQual == "Fa"] = 1

# Group for FireplaceQu
df$fuoco[FireplaceQu == "Ex"] = 5
df$fuoco[FireplaceQu == "Gd"] = 4
df$fuoco[FireplaceQu == "TA"] = 3
df$fuoco[FireplaceQu == "Fa"] = 2
df$fuoco[FireplaceQu == "Po"] = 1
df$fuoco[is.na(FireplaceQu)] = 0

# Group for GarageType
df$t_macchina[GarageType=="Attchd"] = 6
df$t_macchina[GarageType=="BuiltIn"] = 5
df$t_macchina[GarageType=="2Types"] = 4
df$t_macchina[GarageType=="Basment"] = 3
df$t_macchina[GarageType=="CarPort"] = 2
df$t_macchina[GarageType=="Detchd"] = 1
df$t_macchina[is.na(GarageType)] = 0

# Group for GarageFinish
df$f_macchina[GarageFinish=="Fin"] = 3
df$f_macchina[GarageFinish=="RFn"] = 2
df$f_macchina[GarageFinish=="Unf"] = 1
df$f_macchina[is.na(GarageFinish)] = 0

# Group for GarageQual
df$q_macchina[GarageQual == "Ex"] = 5
df$q_macchina[GarageQual == "Gd"] = 4
df$q_macchina[GarageQual == "TA"] = 3
df$q_macchina[GarageQual == "Fa"] = 2
df$q_macchina[GarageQual == "Po"] = 1
df$q_macchina[is.na(GarageQual)] = 0

# Group for GarageCond
df$q2_macchina[GarageCond == "Ex"] = 5
df$q2_macchina[GarageCond == "Gd"] = 4
df$q2_macchina[GarageCond == "TA"] = 3
df$q2_macchina[GarageCond == "Fa"] = 2
df$q2_macchina[GarageCond == "Po" ] = 1
df$q2_macchina[is.na(GarageCond)] = 0

# Group for PavedDrive
df$vial_asf[PavedDrive == "Y"] = 3
df$vial_asf[PavedDrive == "N"] = 2
df$vial_asf[PavedDrive == "P"] = 1
df$vial_asf[is.na(PavedDrive)] = 0

# Group for Functional
df$casa_f[Functional=="Typ"] = 7
df$casa_f[Functional=="Mod"] = 6
df$casa_f[Functional=="Maj1"] = 5
df$casa_f[Functional=="Maj2"] = 4
df$casa_f[Functional=="Min1"] = 3
df$casa_f[Functional=="Min2"] = 2
df$casa_f[Functional=="Sev"] = 1
df$casa_f[is.na(Functional)] = 0

# Group for PoolQC
df$piscina_q[PoolQC =="Ex"] = 3
df$piscina_q[PoolQC =="Gd"] = 2
df$piscina_q[PoolQC =="Fa"] = 1
df$piscina_q[is.na(PoolQC)] = 0

# Group for Fence
df$cancello_p[Fence =="GdPrv"] = 4
df$cancello_p[Fence =="GdWo"] = 3
df$cancello_p[Fence =="MnPrv"] = 2
df$cancello_p[Fence =="MnWw"] = 1
df$cancello_p[is.na(Fence)] = 0

# Group for Alley
df$alley_p[Alley =="Pave"] = 2
df$alley_p[Alley =="Grvl"] = 1
df$alley_p[is.na(Alley)] = 0

# Group for SaleType
df$tipologia_vendita[SaleType=="New"] = 9
df$tipologia_vendita[SaleType == "Con"] = 8
df$tipologia_vendita[SaleType =="CWD"] = 7
df$tipologia_vendita[SaleType =="ConLI"] = 6
df$tipologia_vendita[SaleType=="WD"] = 5
df$tipologia_vendita[SaleType=="COD"] = 4
df$tipologia_vendita[SaleType =="ConLw"] = 3
df$tipologia_vendita[SaleType=="ConLD"] = 2
df$tipologia_vendita[SaleType =="Oth"] = 1

# Group for SaleCondition
df$s_vendita[SaleCondition=="Partial"] = 6
df$s_vendita[SaleCondition=="Normal"] = 5
df$s_vendita[SaleCondition == "Alloca"] = 4
df$s_vendita[SaleCondition =="Family"] = 3
df$s_vendita[SaleCondition=="Abnorml"] = 2
df$s_vendita[SaleCondition =="AdjLand"] = 1

# Group for Condition1
df$locazione1[Condition1=="PosA"] = 9
df$locazione1[Condition1 =="PosN"] = 8
df$locazione1[Condition1 =="Artery"] = 7
df$locazione1[Condition1 =="Norm"] = 6
df$locazione1[Condition1 =="Feedr"] = 5
df$locazione1[Condition1 =="RRAe"] = 4
df$locazione1[Condition1 =="RRAn"] = 3
df$locazione1[Condition1 =="RRNe"] = 2
df$locazione1[Condition1 =="RRNn"] = 1

# Group for Condition2
df$locazione2[Condition2=="PosA"] = 8
df$locazione2[Condition2 =="PosN"] = 7
df$locazione2[Condition2 =="Artery"] = 6
df$locazione2[Condition2 =="Norm"] = 5
df$locazione2[Condition2 =="Feedr"] = 4
df$locazione2[Condition2 =="RRAe"] = 3
df$locazione2[Condition2 =="RRAn"] = 2
df$locazione2[Condition2 =="RRNn"] = 1

# Group for MSZoning
df$luogo[MSZoning =="FV"] = 5
df$luogo[MSZoning=="RL"] = 4
df$luogo[MSZoning =="RH"] = 3
df$luogo[MSZoning =="RM"] = 2
df$luogo[MSZoning =="C (all)"] = 1

# detach is the inverse function of attach
detach(df)

return(df)
}

```

##Drop Variables

Now, we dropped off the variables that are no longer needed.

```{r Drop_Variable_Function}
drop_var <- function(df)
{
# xx is a copy of df dataset without the variables that we decide to delete
xx = df %>% select(-c(Street,LotShape,LandContour,Utilities,LotConfig,LandSlope,Neighborhood,Condition1,Condition2,BldgType,HouseStyle,RoofStyle,RoofMatl,Exterior1st,Exterior2nd,MasVnrType,ExterQual,ExterCond,Foundation,BsmtQual,BsmtCond,BsmtExposure,BsmtFinType1,BsmtFinType2,Heating,HeatingQC,CentralAir,Electrical,KitchenQual  ,FireplaceQu  ,GarageType  ,GarageFinish  ,GarageQual  ,GarageCond  ,PavedDrive  ,Functional  ,PoolQC  ,Fence  ,MiscFeature  ,SaleType  ,SaleCondition  ,MSZoning  ,Alley  ))

# return xx dataset
return(xx)
}
```

##Drop NA

We fill the NA values in our variables with some reasonable values, using different methods.

```{r drop_NA_Function}
drop_NA <- function(df)
{
# NA = 0 when NA meant "absence of feature"
df$BsmtFinSF1[is.na(df$BsmtFinSF1)] = 0
df$BsmtFinSF2[is.na(df$BsmtFinSF2)] = 0
df$BsmtUnfSF[is.na(df$BsmtUnfSF)] = 0
df$TotalBsmtSF[is.na(df$TotalBsmtSF)] = 0
df$BsmtFullBath[is.na(df$BsmtFullBath)] = 0
df$BsmtHalfBath[is.na(df$BsmtHalfBath)] = 0
df$GarageCars[is.na(df$GarageCars)] = 0
df$GarageArea[is.na(df$GarageArea)] = 0
df$egws[is.na(df$egws)] = 0
df$cucina[is.na(df$cucina)] = 0


# For this variables we substituted the NA values with the variable's mode
df$mura1[is.na(df$mura1)] = unname(which(table(df$mura1)==max(table(df$mura1))))
df$mura2[is.na(df$mura2)] = unname(which(table(df$mura2)==max(table(df$mura2))))
df$luogo[is.na(df$luogo)] = unname(which(table(df$luogo)==max(table(df$luogo))))
df$tipologia_vendita[is.na(df$tipologia_vendita)] = unname(which(table(df$tipologia_vendita)==max(table(df$tipologia_vendita))))


# For the other variables we decided to use "cart" method (it is slow but it works well)
# mice package substitutes the remaining NA values with the best one found with the cart method
auxiliar_train = mice(df, m=1 , maxit = 1 , method = "cart")
df = complete(auxiliar_train,1)

return(df)
}
```

## Interactions 

Here we create new variables, that are interactions between old ones.

```{r interactions_Function}
# Interactions based on correlation
create_interaction <- function(df)
{
# Interactions are created by making the product between the variables that are already in our dataset
df$years_cond =  df$YearBuilt*df$OverallCond
df$ann_q = df$YearBuilt*df$OverallQual
df$BsmtType1Qual = df$q_cantina*df$f1_cantina
df$ann_r_q = df$YearRemodAdd*df$OverallQual 
df$cant_q = df$OverallQual*df$TotalBsmtSF 
df$massVnrCond =  df$MasVnrArea*df$c_est
df$bagn_q = df$OverallQual*df$FullBath 
df$qual_zon = df$OverallQual*df$GrLivArea 
df$massVnrQual =  df$MasVnrArea*df$q_est
df$outside_q = df$OverallQual*df$c_est
df$BsmtType1Cond = df$c_cantina*df$f1_cantina


# The df datset, that we return in the function, is the one composed by both new and old variables
return(df)
}
```

#Work On Train 

Here we apply the function built previously to clean the variables in the train dataset.
We overwrite the previous train dataset with the new one, in which we apply "clean_data" function, in order to avoid the presence of too many variables in the Global Environment.

```{r Clean_Train}
train <- clean_data(train)
```

Here we apply the function built previously to drop the variables no longer needed in the train dataset.

```{r Drop_Variable_Train}
train <- drop_var(train)
```

Here we apply the function built previously to delete the NAs in the train dataset.

```{r drop_NA_Train}
train <- drop_NA(train)
```

Here we use the "create_interaction" function to create new variables based on correlation in the train dataset.

```{r interactions_Train}
train <- create_interaction(train)
```

Remove outliers respect of GrLivArea in the train dataset.

```{r remove_outliers_Train}
train = train[-which(train$GrLivArea > 4000 & train$SalePrice < 3e+05),]
```

#Linear Model

Here we create a new dataset that is a copy of the train dataset, to work with linear regression model without making changes on the original train dataset.

```{r copy_dataset}
train_lin = train
```

Here we standardize the non-binary variables in our "train_lin" dataset except for the SalePrice.

```{r standardization}
# Save SalePrice column in an auxiliar varialbe, because we don't want to standardize it
aux = train_lin$SalePrice
for(i in 2:(ncol(train_lin))){
  # Evaluate the mean and the standard error for each variable in the loop
  std_err=sd(train_lin[,i])
  media = mean(train_lin[,i])
  # Check if the variable is binary
  if ((max(train_lin[,i])!=1) | (min(train_lin[,i])!=0))
  {
    
  # In case of non-binary variable, make the standardization on all the variable elements
  for(j in 1:length(train_lin[,i])){
    train_lin[j,i]=(train_lin[j,i] - media)/std_err
  }
  }
}

# Attach the non standardize SalePrice column in the dataset train_lin
train_lin$SalePrice = aux
```

After the standardization, we replace the original SalePrice column with the logarithm of that column.

```{r log_SalePrice}
train_lin$SalePrice = log(train_lin$SalePrice)
```

Now we have our final dataset, and we build our linear model removing a few variables, which give us multicollinearity.
To choose the variables to remove, we used "backward elimination" algorithm.

This algorithm starts with all candidate variables, testing the deletion of each variable using a chosen model fit criterion (p-value and R^2 adjusted), deleting the variable whose loss gives the most statistically insignificant deterioration of the model fit, and repeating this process until no further variables can be deleted without a statistically significant loss of fit.

```{r lm}
# In our model Y is the SalePrice and X are all the variables in the "train_lin" dataset, except of the ones written with the "-" symbol
modello_lin = lm(SalePrice ~ .-Id -BsmtFinSF1 -BsmtFinSF2 -BsmtUnfSF -GrLivArea , data=train_lin)
```

# Work On Test

Now we do the same things that we made in train dataset on the test one.
Starting by cleaning the data.

```{r Clean_Test }
test <-clean_data(test)
```

Here, we dropped off the variables that are no longer needed.

```{r Drop_Variable_Test}
test <- drop_var(test)
```

We fill the NA values in our variables with some reasonable values, as done in the train dataset.

```{r Drop_NA_Test}
test <- drop_NA(test)
```

Here we use the "create_interaction" function to create new variables based on correlation in the test dataset.

```{r interactions_Test}
# Interactions based on correlation
test <- create_interaction(test)
```

# Linear Model Prediction

Here we create a new dataset that is a copy of the test dataset, to work with linear regression model without making changes on the original test dataset.

```{r copy_Test}
test_lin = test
```

As done for the train dataset, we standardize the dataset.
In this dataset there isn't the SalePrice column, and so we don't have to remove it before the standardization.

```{r test_standardization}
for(i in 2:(ncol(test_lin)))
  {
  # Evaluate the mean and the standard error for each variable in the loop
  std_err=sd(test_lin[,i])
  media = mean(test_lin[,i])
  # Check if the variable is binary
  if ((max(test_lin[,i])!=1) | (min(test_lin[,i])!=0))
  {
  # In case of non-binary variable, make the standardization on all the variable elements
  for(j in 1:length(test_lin[,i])){
    test_lin[j,i]=(test_lin[j,i] - media)/std_err
  }
  }
}
```

Here we predict the SalePrice of the test dataset using our linear model (built in "modello_lin").
At the end we also create an .csv file with the result.

```{r write_csv}
# Add SalePrice column to train_lin dataset, using as value the exponential of the predicted SalePrice, using our linear model

# We use the exponential because we did the logarithm of the SalePrice previously
test_lin$SalePrice = exp(predict(modello_lin, newdata = test_lin))
test_lin %>%
  select(Id, SalePrice )%>%
  # Write the csv file with two columns: Id and SalePrice, as asked in Kaggle competition
  write.csv(file = "lm1.csv", row.names = F)
```

# XG-BOOST

We return working on the original test and train dataset, applying XGBoost method. XGBoost is an implementation of gradient boosted decision trees designed for speed and performance.
We start by working on the train dataset to estimate the parameters.

```{r xboost}
# Create a vector with all the variables'names except SalePrice
# In our Train dataset SalePrice is the 38th column
variable_name = c(colnames(train[,c(2:37, 39:length(train))]))

# Transform train dataset in a sparse matrix
# This is the format needed by xboost method
train_sparse_matrix= as(as.matrix(train, rownames.force=NA),"sparseMatrix")

trainD = xgb.DMatrix(data = train_sparse_matrix[,variable_name], label = train_sparse_matrix[,"SalePrice"]) 

# Define parameters for x-boost
features = list(colsample_bytree = .7, subsample = .7, booster = "gbtree", max_depth = 7 ,eta = 0.02, eval_metric = "rmse",objective="reg:linear")

# Train the Xgboost model
bstSparse =xgb.train(params = features,data = trainD, nrounds = 1000, watchlist = list(train = trainD),verbose = TRUE,print_every_n = 50,nthread = 2)

predict=as.data.frame(test)
# Transform the test dataset in a matrix 
predict_matrix= as.matrix(predict, rownames.force=NA)

# Transform test dataset in a sparse matrix
predicting = as(predict_matrix, "sparseMatrix")

```

Actually do the predicting on the test dataset.

```{r finalpredict_xboost}
# Make the prediction on the test dataset (that now is a sparsematrix)
boostPred = as.data.frame(as.matrix(predict(bstSparse, predicting[,variable_name])))

# Change column name of boostPred dataframe
colnames(boostPred) = "prediction"

# Add a column to an existing dataframe
boost_Out = cbind(predict, boostPred) 

# Create a new dataframe with only Id and SalePrice columns 
#In this dataframe SalePrice is estimated using xboost method
final_df_xboost = data.frame(Id = boost_Out$Id, SalePrice = boost_Out$prediction)

# Here we create the .csv file
write.csv(final_df_xboost, file = "xboost1.csv", row.names = F)
```

#LASSO

Now we estimate our third model, that is the Lasso Regression. Lasso regularization work by adding a penalty term to the log-likelihood function, called $\lambda$.
In this chunk we’ll use the function cv.glmnet, which automatically performs a grid search to find the optimal value of $\lambda$.
We start by working on the train dataset to estimate the parameters also in this case.

```{r Lasso_Prediction}
# Create a copy of the train dataset
train_lasso <- train

# Drop the SalePrice column
train_lasso$SalePrice <- NULL

# Transform this new dataset in a matrix
# The glmnet() function need a matrix in input
train_lasso=as.matrix(train_lasso)

# Use the cross-validation method to estimate the parameters
fit2 <-cv.glmnet(x = train_lasso, y = log(train$SalePrice + 1))

# Create a new dataset, that is a copy of the original test
# Also this new dataset has to be a matrix
test_lasso <- as.matrix(test)

# Make the estimation using the parameters evaluate before
ris2 <- data.frame(exp(predict(fit2, s="lambda.min", newx=test_lasso)) - 1)

# Create a new dataframe with only two column:
# 1) Id
# 2) SalePrice (estimate using Lasso algorithm)
fina = data.frame(Id = test$Id, SalePrice = ris2)

names(fina) <- c("Id","SalePrice")
write.csv(fina, file = "Lasso.csv", row.names = F)
```

# Final result

Now we evaluate the weighted mean between the three previous methods with different weights.  
We save the final result in a .csv file, called "pred.csv".
This is our final result, and this file is the one that has to be submitted.
We tried to run our code on different computers, obtaining different results making submission of "pred.csv".
We chose the best one.

```{r final_pred}
# Create a new dataframe where SalePrice column is the average mean of SalePrice obtained with the three methods described above
subcomb = data.frame(Id = boost_Out$Id, SalePrice = 0.68*boost_Out$prediction+0.10*test_lin$SalePrice + 0.22*ris2)

names(subcomb)=c("Id","SalePrice")
write.csv(subcomb, file = "pred.csv", row.names = F)
```